---
title: "UM6SS Thesis Defense"
subtitle: "A personalized Quarto beamer deck"
author: "Your Name"
institute: "Université Mohammed VI des Sciences et de la Santé"
date: last-modified
format:
  beamer:
    theme: default
    colortheme: default
    aspectratio: 169
    navigation: horizontal
    include-in-header: slides-in-header.tex
execute:
  echo: false
---

## Overview

Université Mohammed VI des Sciences et de la Santé

Use this deck for a thesis defense, progress update, or internal presentation. It shares its color palette with the thesis PDF (`_extensions/quarto-thesis/partials/in-header.tex`) and its results with `Chapters/Chapter2.qmd`.

## Presentation flow

1. Research context
2. Objectives
3. Methods
4. Results
5. Discussion and next steps

## Branded template

- A consistent red UM6SS visual identity, matching the thesis PDF.
- A title slide that carries the same school logo.
- Simple layouts that work on projectors and laptops.

## Results

The figure and table below come straight from `R/shared-results.R`, the same script used in the "Example results" section of Chapter 2, so the numbers on the slide can never drift from the numbers in the manuscript.

```{r}
#| label: setup-shared-results
source("R/shared-results.R")
```

```{r}
#| label: fig-slide-results
#| fig-cap: "Example primary outcome by study group."
example_plot()
```

## Results table

```{r}
#| label: tbl-slide-results
knitr::kable(example_table())
```

## Closing

Thank you.

<!-- For the full "how to build slides with Quarto" teaching session (one
concept per slide: images, figures, code, tables, layout, citations,
rendering), see quarto-slides-course.qmd. -->
